\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{MetaKicks\\
- Virtual Price Tracking LG Styler ShoeCase 
}

\author{\IEEEauthorblockN{Kwon Jihyun 2018007383}
\IEEEauthorblockA{\textit{College of engineering,} \\
\textit{Hanyang University}\\
\textit{Dept. of Information system}\\
Seoul, Korea \\
nahoo0705@hanyang.ac.kr}
\and
\IEEEauthorblockN{Kim Younghwan 2018007410}
\IEEEauthorblockA{\textit{College of engineering,} \\
\textit{Hanyang University}\\
\textit{Dept. of Information system}\\
Seoul, Korea \\
wizde20@hanyang.ac.kr}
\and
\IEEEauthorblockN{Lee Jiyun 2018007692}
\IEEEauthorblockA{\textit{College of engineering,} \\
\textit{Hanyang University}\\
\textit{Dept. of Information system}\\
Seoul, Korea \\
dlwldbs9764@hanyang.ac.kr}
\and
\IEEEauthorblockN{Jeong Youngho 2018007765}
\IEEEauthorblockA{\textit{College of engineering,} \\
\textit{Hanyang University}\\
\textit{Dept. of Information system}\\
Seoul, Korea \\
zer0kola321@hanyang.ac.kr}
}

\maketitle

\begin{abstract}
\textit{As the culture of collecting expensive designer, luxury and limited-edition sneakers grows among the MZ generation – Millennials and Gen Z – LG’s internal research found that these ‘sneakerheads’ would benefit greatly from a solution that not only made their cherished shoes stand out more, but also provided them with the optimal care. and LG provides LG ThinQ applications to connect its home appliances and consumers and provide consumers with a better experience. So our team thought that it would be good to virtualize the ShoeCase and manage it on the ThinQ app. By storing nft sneakers in a MetaKicks, nft, which exists only virtually, is collected as if it were stored in a LG Styler ShoeCase. In addition, the limited edition of the shoe resell market has grown a lot, and we decided to create this service to check the resale market price of shoes in real time. Finally, we thought that the culture of collecting shoes could be further activated by taking out the shoe case that was only in my room on the web and creating a culture to share each other's shoes collections.}\end{abstract}


\begin{table}[h!]
\caption{Role Assignments}
\def\arraystretch{1.24} \small
    \begin{tabular}{|p{1.8cm}|p{1.4cm}|p{4.4cm}|}
        \hline
        Roles & Name & Task description and etc. \\ \hline
         User \par Customer & Kwon \par Jihyun & User/Customer contemplates what functions should be added from the perspective of users or customers. In addition, the 
 application automatically identifies shoes in LG Styler Shoecase and track realtime resell prices.\\ \hline
         
        Software \par Developer& Kim \par Younghwan  & They understand demand and requirement of application. They test the overall application from customers’ point of view and report error and bug. They strive to maximize user experience by considering UI / UX. \\ \hline
        
        Software \par Developer & Lee Jiyun  & Software developers think about the software in general. They design and implement the requirements of application. They also strive to satisfy users and customers. \\ \hline
        
        Development \par manager & Jeong Youngho & Development manager manages the overall project. They strive to meet the needs of customers. They collect the feedback from users. After collecting feedback, they advise software developers to improve application quality. \\ \hline
    \end{tabular}
\end{table}

\section{Introduction}
\subsection{Motivation}
Shoe cases so far are made of plastic and can only function as storage and display shoes. But The LG Styler ShoeCase creates the ideal environment for storing shoes by protecting against humidity and fabric-discoloring UV light, the Styler ShoeCase represents a great way for shoe enthusiasts to show-off their favorite pairs, offering interior features such as a 360-degree rotating turntable to increase the value as a collection rather than just shoes. 
Nft shoes are stored online, and real shoes are stored only in the shoe rack and managed separately. By using this, these two collections are managed by one app. We thought it would be good to share the collection, including nft shoes, with various people to further boost the shoe collection culture.
So we make this service by paying attention to the value of the collection. It check the fluctuating resell market price in real time using Kream or StockX's API, Korea and USA's leading sneakers trade site, and sharing each other's collections through this service.


\subsection{problem statement}
\begin{itemize}
\item In The case of limited-edition shoes, prices fluctuate significantly over time or depending on events, so collectors who own several shoes find it difficult to know the value of the collections at once.
\item The shoe case so far is just a plastic drawer. There is only a storage function and the function of the exhibition is inferior.
\item We are managing NFT and real shoes separately
\item There is no means to check the shoes stored at home outside.
\item You can't see other people's sneakers collection unless you go their home.
\end{itemize}

\subsection{Research of any relative software}

{Kream} \\ It is a transaction brokerage platform that connects sellers and buyers anonymously. Similar to trading methods such as stocks and cryptocurrencies, it consists of presenting the price the seller wants to sell and accepting the price. Due to the nature of the asking price transaction, used goods are not handled because the premise that all items are the same is necessary. The main trading items are limited edition products such as clothing and fashion miscellaneous goods, and can be seen as a commonly referred to as a resale trading platform. Unlike general direct transaction platforms, products are traded through the KREAM inspection center. When the seller sends the product to the KREAM inspection center, the KREAM inspects it and sends it to the buyer.\\

{StockX} \\ It serves as an online marketplace, facilitating auctions between sellers and buyers, then collecting transaction and payment fees. Sellers send purchased items to StockX facilities for inspection and verification, then authenticated products are shipped to buyers. StockX features a "stock market-like" variable pricing framework and discloses price histories for specific items. StockX is most known for sneakers and streetwear but also carries other clothing and accessories such as handbags and watches.\\

{LG ThinQ} \\ A representative home appliance management app that provides smart home services based on AI. With this application, you can control not only home appliances, but also all parts of the house, as well as check product status and malfunctions anytime, anywhere. In a situation in which the market environment is rapidly changing from 'supplier-centered' to 'consumer-centered, LG is providing these services, believing that the role of AI technology has grown.\\

\section{Requirement Analysis}

\subsection{Login}
It supports Google login and Apple login by linking Firebase and Flutter. If the login is successful, you will be taken to the main page.\\

\subsection{Main Page}
Users can check the functions in the app at once on the main page. \\
\begin{enumerate}
    \item My ShoeCase\\
    \item Finding Other User\\
    \item Favorite ShoeCase\\
\end{enumerate}

\subsection{My ShoeCase}
My ShoeCase page visualizes LG Styler ShoeCase on the web. There is no Shoes in the first entry. There is a pop-up page that writes the name or serial number of the ShoeCase product, then a virtual ShoeCases will be created according to the number of rooms and size of the ShoeCase. A user can nickname the user's ShoeCase.
\\
\begin{enumerate}
    \item Register Shoes by Style Code: There is a button for registering shoes in each section of the ShoeCase. When the user clicks the button, a pop-up window appears, and the user can search style code on the shoes site and register the shoes. For NFT shoes, there is an NFT shoe registration button. When you click the button, a pop-up window appears, and if you enter NFT information for the shoes, you will be registered in the virtual shoe closet like normal shoes.
\\
    \item Registered Shoes Information: The name and real-time resell price of the shoes displayed on the virtual ShoeCase. When the user clicks the shoes, The product’s site will appear to show the information of shoes linking with the shoes site.
\\
    \item Public/Private Setting: There is a checkbox to determine to show the user's ShoeCase
\\
    \item The number of heart: Those who have seen user's ShoeCase and like it press the heart. Total number of hearts is displayed.
\\
\end{enumerate}

\subsection{Finding Other User}

Other people's ShoeCase is listed only for those allowed to reveal their ShoeCase. The list displays the user's name and the nickname of the ShoeCase. When the user clicks the name of the person the user wants to see, the page switches to the that person's ShoeCase page.
\\
\begin{enumerate}
	\item Search Someone's ShoeCase: You can search the user's nickname and view the published ShoeCase.
\\
	\item Recommendation: List ShoeCase by number of hearts. 
\\
\end{enumerate}

\subsection{Favorite ShoeCase}

There is no ShoeCases in the first entry. If you click the heart button on your favorite ShoeCase among other people's ShoeCase. The ShoeCases are registered in my favorites. And Click the ShoeCase button to go to the user's ShoeCase. Sends a notification whenever new shoes are added to your favorite ShoeCase. 
\\
\begin{enumerate}
	\item Favorite ShoeCase lists: List your favorite ShoeCases.
	\\
	\item Visit Someone's ShoeCase: If you click the ShoeCase's nickname on the list, app shows that user's ShoeCase Page. 
\\
\end{enumerate}




\end{document}